---
title: "final project"
output: html_document
date: "2022-11-29"
---
---
title: "final project"
output: html_document
date: "2022-11-29"
---

# Filtered the Raw Dataset for project
```{r}
library(stringr)
final = data.frame(read.csv("dataset/train.csv"))
df = final
#df = subset(final, Month=="January")

library(dplyr)
names(df)

df <- df[,c("Credit_Score","Credit_Mix","Credit_History_Age","Monthly_Balance","Num_of_Delayed_Payment","Total_EMI_per_month","Age","Outstanding_Debt","Num_Bank_Accounts","Num_Credit_Card","Num_of_Loan","Num_Credit_Inquiries","Monthly_Inhand_Salary","Amount_invested_monthly","Annual_Income","Month")]

summary(df)
str(df)
# Credit_Score (o)
# Credit_Mix (o),Credit_History_Age, Monthly_Balance (o)
# Num_of_Delayed_Payment (o), Total_EMI_per_month (o), Age(o), Outstanding_Debt
# Num_Bank_Accounts, Num_Credit_Card, Num_of_Loan (o), Num_Credit_Inquiries
# Occupation, Montly_Inhand_Salary, Annual_Income (o), Amount_invested_monthly
```

# Data Cleaning
```{r}
## "Occupation"
#df$Occupation <- replace(df$Occupation, df$Occupation=="_______", NA)
#df$Occupation <- as.factor(df$Occupation)
#df$Occupation = as.numeric(df$Occupation)

## "Amount_invested_monthly"
df$Amount_invested_monthly = as.numeric(df$Amount_invested_monthly)
#df["Total_EMI_per_month"] <- round(df["Total_EMI_per_month"], digits = 2)

## "Outstanding_Debt"
df$Outstanding_Debt = str_replace(df$Outstanding_Debt,"_","")
df$Outstanding_Debt = as.numeric(df$Outstanding_Debt)

## "Credit_History_Age"
library(stringr)
df$Credit_History_Age = str_replace(df$Credit_History_Age,"Years and","")
df$Credit_History_Age = str_replace(df$Credit_History_Age,"Months","")
df$Credit_History_Age = str_replace(df$Credit_History_Age," ",".")
df$Credit_History_Age = str_replace(df$Credit_History_Age," ","")
df$Credit_History_Age = as.numeric(df$Credit_History_Age)

## "Age"
df$Age <- gsub("[[:punct:]]", "", df$Age)
df$Age <- as.integer(df$Age)
# Filtered out a group age under 18 and greater than 100
df <- df[(df$Age > 17) & (df$Age < 100),]

## "Annual_Income"
#Removed Special Characters & Changed the data type into "num" & Rounded
df$Annual_Income <- as.numeric(sub("_", "", df$Annual_Income))

## "Num_of_Delayed_Payment"
# Removed Special Characters & Changed the data type from "char" to "int"
df$Num_of_Delayed_Payment <- gsub("[[:punct:]]", "", df$Num_of_Delayed_Payment)
df$Num_of_Delayed_Payment <- as.integer(df$Num_of_Delayed_Payment)

## "Num_of_Loan" 
# Removed Special Characters & Changed the data type from "char" to "int"
df$Num_of_Loan <- gsub("[[:punct:]]", "", df$Num_of_Loan)
df$Num_of_Loan <- as.integer(df$Num_of_Loan)
# Removed value below 0 
df <- df[df['Num_of_Loan'] >= 0, ]

## "Credit_Mix"
# Removed Special Characters 
# Converted "char" into "int" from "Good" to 3, "Standard" to 2, and "Bad" to 1
df <- df[df['Credit_Mix'] != "_",]
df$Credit_Mix[df$Credit_Mix == 'Bad'] <- 1
df$Credit_Mix[df$Credit_Mix == 'Standard'] <- 2
df$Credit_Mix[df$Credit_Mix == 'Good'] <- 3
df$Credit_Mix <- as.integer(df$Credit_Mix)

## "Total_EMI_per_month"
df["Total_EMI_per_month"] <- round(df["Total_EMI_per_month"], digits = 2)

## "Credit_score"
# Removed Special Characters
df <- df[df['Credit_Score'] != "_",]
df$Credit_Score[(df$Credit_Score == 'Poor')] <- 1
df$Credit_Score[(df$Credit_Score == 'Standard')] <- 2
df$Credit_Score[(df$Credit_Score == 'Good')] <- 3
df$Credit_Score <- as.integer(df$Credit_Score)

## "Monthly_Balance"
# Converted into "int" and rounded 
df$Monthly_Balance <- as.integer(df$Monthly_Balance)
df["Monthly_Balance"] <- round(df["Monthly_Balance"], digits = 2)

## "Month"
df$Month[(df$Month == 'January')] <- 1
df$Month[(df$Month == 'February')] <- 2
df$Month[(df$Month == 'March')] <- 3
df$Month[(df$Month == 'April')] <- 4
df$Month[(df$Month == 'May')] <- 5
df$Month[(df$Month == 'June')] <- 6
df$Month[(df$Month == 'July')] <- 7
df$Month[(df$Month == 'August')] <- 8
df$Month <- as.integer(df$Month)
```

## Removed NA from data
```{r}
df = na.omit(df)
```

## Removed Outliers 
```{r}
library(ezids)
df = outlierKD2(df, Credit_History_Age, rm=T)
df = outlierKD2(df, Monthly_Balance, rm=T)
df = outlierKD2(df, Num_of_Delayed_Payment, rm=T)
df = outlierKD2(df, Total_EMI_per_month, rm=T)
df = outlierKD2(df, Age, rm=T)
df = outlierKD2(df, Outstanding_Debt, rm=T)
df = outlierKD2(df, Num_Bank_Accounts, rm=T)
df = outlierKD2(df, Num_Credit_Card, rm=T)
df = outlierKD2(df, Num_of_Loan, rm=T)
df = outlierKD2(df, Num_Credit_Inquiries, rm=T)
df = outlierKD2(df, Monthly_Inhand_Salary, rm=T)
df = outlierKD2(df, Amount_invested_monthly, rm=T)
df = outlierKD2(df, Annual_Income, rm=T)
str(df)
```

## Removed NA from data
```{r}
df = na.omit(df)
```

# EDA

## Histogram
```{r, histograms}

df$Credit_Score <- as.factor(df$Credit_Score)

library(ggplot2)

ggplot(df, aes(x=Credit_Mix, fill = Credit_Score, colour = Credit_Score)) +
  geom_histogram(alpha = 0.7, bins = 3)+
  labs(title="Histogram of Credit_Mix")

ggplot(df, aes(x=Credit_History_Age, fill = Credit_Score, colour = Credit_Score)) +
  geom_histogram(alpha = 0.7)+
  labs(title="Histogram of Credit_History_Age")

ggplot(df, aes(x=Monthly_Balance, fill = Credit_Score, colour = Credit_Score)) +
  geom_histogram(alpha = 0.7)+
  labs(title="Histogram of Monthly_Balance")

ggplot(df, aes(x=Num_of_Delayed_Payment, fill = Credit_Score, colour = Credit_Score)) +
  geom_histogram(alpha = 0.7)+
  labs(title="Histogram of Num_of_Delayed_Payment")

ggplot(df, aes(x=Total_EMI_per_month, fill = Credit_Score, colour = Credit_Score)) +
  geom_histogram(alpha = 0.7)+
  labs(title="Histogram of Total_EMI_per_month")

ggplot(df, aes(x=Age, fill = Credit_Score, colour = Credit_Score)) +
  geom_histogram(alpha = 0.7)+
  labs(title="Histogram of Age")

ggplot(df, aes(x=Outstanding_Debt, fill = Credit_Score, colour = Credit_Score)) +
  geom_histogram(alpha = 0.7)+
  labs(title="Histogram of Outstanding_Debt")

ggplot(df, aes(x=Num_Bank_Accounts, fill = Credit_Score, colour = Credit_Score)) +
  geom_histogram(alpha = 0.7, bins = 12)+
  labs(title="Histogram of Num_Bank_Accounts")

ggplot(df, aes(x=Num_Credit_Card, fill = Credit_Score, colour = Credit_Score)) +
  geom_histogram(alpha = 0.7, bins = 12)+
  labs(title="Histogram of Num_Credit_Card")

ggplot(df, aes(x=Num_of_Loan, fill = Credit_Score, colour = Credit_Score)) +
  geom_histogram(alpha = 0.7, bins = 12)+
  labs(title="Histogram of Num_of_Loan")

ggplot(df, aes(x=Num_Credit_Inquiries, fill = Credit_Score, colour = Credit_Score)) +
  geom_histogram(alpha = 0.7, bins = 15)+
  labs(title="Histogram of Num_Credit_Inquiries")

ggplot(df, aes(x=Monthly_Inhand_Salary, fill = Credit_Score, colour = Credit_Score)) +
  geom_histogram(alpha = 0.7)+
  labs(title="Histogram of Monthly_Inhand_Salary")

ggplot(df, aes(x=Annual_Income, fill = Credit_Score, colour = Credit_Score)) +
  geom_histogram(alpha = 0.7)+
  labs(title="Histogram of Annual_Income")

df$Credit_Score <- as.integer(df$Credit_Score)

```

## Chi-squared
```{r}
mix = table(df$Credit_Mix, df$Credit_Score)
rownames(mix) <- c("Bad","Standard","Good")
xkabledply(mix, title="Contingency table for Credit_Mix vs Credit_Score")

chitest = chisq.test(mix)
print(chitest)
```

## Boxplots
```{r}
library(ggplot2)
df$Credit_Score <- factor(df$Credit_Score , levels=c('1', '2', '3'))

# Credit Score & Monthly_Balance 
ggplot(df, aes(x=Credit_Score, y=Monthly_Balance)) + geom_boxplot( color=c("red","green","blue")) + 
  labs(title="Boxplot of the Monthly Balance with different Credit Scores", x="Credit Score", y = "Monthly Balance")

# Credit Score & Credit_History_Age
ggplot(df, aes(x=Credit_Score, y=Credit_History_Age)) + geom_boxplot( colour=c("red","green","blue")) + 
  labs(title="Boxplot of the Credit History Age with different Credit Scores", x="Credit Score", y = "Credit History Age")

# Credit Score & Num_Credit_Card
ggplot(df, aes(x=Credit_Score, y=Num_Credit_Card)) + geom_boxplot( colour=c("red","green","blue")) + 
  labs(title="Boxplot of the Number of Credit Cards with different Credit Scores", x="Credit Score", y = "Number of Credit Cards")

# Credit Score & Num_Credit_Inquiries
ggplot(df, aes(x=Credit_Score, y=Num_Credit_Inquiries)) + geom_boxplot( colour=c("red","green","blue")) + 
  labs(title="Boxplot of the Number of Credit Inquiries with different Credit Scores", x="Credit Score", y = "Number of Credit Inquiries")

# Credit Score & Outstanding_Debt 
ggplot(df, aes(x=Credit_Score, y=Outstanding_Debt)) + geom_boxplot( colour=c("red","green","blue")) + 
  labs(title="Boxplot of the Outstanding Debt with different Credit Scores", x="Credit Score", y = "Outstanding Debt")

df$Credit_Score <- as.integer(df$Credit_Score)
```

## ANOVA
```{r}
# Credit Score & Monthly_Balance 
anova1 = aov(Monthly_Balance ~ Credit_Score, data=df)
anova1
names(anova1)
xkabledply(anova1, title = "ANOVA result summary the Monthly Balance between Credit Score")


# Credit Score & Credit_History_Age
anova2 = aov(Credit_History_Age ~ Credit_Score, data=df)
anova2
names(anova2)
xkabledply(anova2, title = "ANOVA result summary the Credit History Age between Credit Score")


# Credit Score & Num_Credit_Card
anova3 = aov(Num_Credit_Card ~ Credit_Score, data=df)
anova3
names(anova3)
xkabledply(anova3, title = "ANOVA result summary the Numer of Credit Cards between Credit Score")


# Credit Score & Num_Credit_Inquiries
anova4 = aov(Num_Credit_Inquiries ~ Credit_Score, data=df)
anova4
names(anova4)
xkabledply(anova4, title = "ANOVA result summary the Numer of Credit Inquiries between Credit Score")

# Credit Score & Outstanding_Debt
anova5 = aov(Outstanding_Debt ~ Credit_Score, data=df)
anova5
names(anova5)
xkabledply(anova5, title = "ANOVA result summary the Outstanding Debt between Credit Score")
```

## Correlation Table
```{r}
loadPkg("corrplot")
dfscale = data.frame(scale(df))
str(dfscale)
dfcor = cor(dfscale,use='complete.obs') 
dfcor
corrplot.mixed(dfcor)
corrplot(dfcor, type = "upper", order = "hclust", tl.col = "black", tl.srt = 45)
```

# SMART Question 1
Five independent variables - payment history, amounts owed, length of credit history, new credit, and credit mix - are known to affect our credit score. Do these (above listed) five independent variables affect the credit score?

Note: Although variables used to calculate the credit score/fico score are five, we have only three out of five variables so will use three for our analysis.

```{r}
fit <- lm(Credit_Score ~ Monthly_Balance +Credit_History_Age+Credit_Mix, data = dfscale)
summary(fit)
```

# Q1 Answer
According to the result, we can see that monthly balance, credit history age and credit mix significantly increase the credit score. 

# SMART Question 2
We include more variables including the variables used in previous analysis – number of credit cards, bank accounts, loans, credit inquiries, and monthly in-hand salary – in our model. Which model is considered the best fit model? 

```{r}
### Featrue Selection
loadPkg("leaps")
reg1 <- regsubsets(Credit_Score~. , data = dfscale, nvmax = 10, nbest = 2, method ="exhaustive")
summary(reg1)
res.sum <- summary(reg1)
data.frame(
  Adj.R2 = which.max(res.sum$adjr2),
  CP = which.min(res.sum$cp),
  BIC = which.min(res.sum$bic))

plot(reg1, scale = "adjr2", main = "Adjusted R^2")
plot(reg1, scale = "r2", main = "R^2")
plot(reg1, scale = "bic", main = "BIC")
plot(reg1, scale = "Cp", main = "Cp")

### Forward Selection
reg.forward10 <- regsubsets(Credit_Score~., data = dfscale, nvmax = 10, nbest = 1, method = "forward")
plot(reg.forward10, scale = "adjr2", main = "Adjusted R^2")
plot(reg.forward10, scale = "bic", main = "BIC")
plot(reg.forward10, scale = "Cp", main = "Cp")
# summary(reg.forward10)

### non-linear model
regnonlin.forward10 <-regsubsets(Credit_Score~., data = dfscale, nvmax = 10, method="forward")
plot(regnonlin.forward10, scale = "adjr2", main = "Adjusted R^2")
plot(regnonlin.forward10, scale = "bic", main = "BIC")
plot(regnonlin.forward10, scale = "Cp", main = "Cp")
summary(regnonlin.forward10)

### Backward Selection
reg.back10 <- regsubsets(Credit_Score~., data = dfscale, method = "backward", nvmax = 10, nbest = 2)
plot(reg.back10, scale = "adjr2", main = "Adjusted R^2")
plot(reg.back10, scale = "bic", main = "BIC")
plot(reg.back10, scale = "Cp", main = "Cp")
summary(reg.back10)

### Sequential Replacement seqrep 
reg.seqrep <- regsubsets(Credit_Score~., data = dfscale, nvmax = 10, nbest = 2 , method = "seqrep")
plot(reg.seqrep, scale = "adjr2", main = "Adjusted R^2")
plot(reg.seqrep, scale = "bic", main = "BIC")
plot(reg.seqrep, scale = "Cp", main = "Cp")

# Alternative plots
loadPkg("car")
summaryRegForward = summary(reg1)
# Adjusted R2
car::subsets(reg1, statistic="adjr2", legend = FALSE, min.size = 2, main = "Adjusted R^2")
# Mallow Cp
subsets(reg1, statistic="cp", legend = FALSE, min.size = 4, main = "Mallow Cp")
abline(a = 1, b = 1, lty = 3)

```

## Better Regression Model with higher adjsted R^2, lower BIC and Cp
```{r}
# Linear Regression Based on Feature Selection Result on Adj R^2
fit1 <- lm(Credit_Score ~ Credit_Mix+Outstanding_Debt+Num_Credit_Card+Num_Credit_Inquiries, data = dfscale)
summary(fit1)

# Linear Regression Based on Feature Selection Result on BIC
fit2 <- lm(Credit_Score ~ Credit_Mix+Num_Credit_Card+Num_Credit_Inquiries, data = dfscale)
summary(fit2)

# Linear Regression Based on Feature Selection Result on Cp: Let's use this logit model.
fit3 <- lm(Credit_Score ~ Credit_Mix+Credit_History_Age+Num_of_Delayed_Payment+Total_EMI_per_month+Age+Outstanding_Debt+Num_Credit_Card+Num_Credit_Inquiries+Amount_invested_monthly+Month, data = dfscale)
summary(fit3)
```

Note: We ran three different models each one have greater R2, lower bic and cp respectively. All three models had the same residual error and adjusted r2. We chose the model with the least BIC because it contains least number of independent variables.

## The Best Regression Model
```{r}
fit4 <- lm(Credit_Score ~ Credit_Mix+Num_Credit_Card+Num_Credit_Inquiries, data = dfscale)
summary(fit4)
```

# Q2 Answer:
After the feature selection process, we tried to build the best fit model having higher adjusted R^2, lower BIC and Cp. The final model's variables are extracted from the BIC result. We can find that credit mix significantly increase the credit score and the number of credit cards and the number of credit inquires have negatively relations with the credit score. So, our takeaway is "Don't ask your credit score too much". 


# SMART Question 3
From the previous analysis in Question 1 we found that three variables - amounts owed, length of credit history, and credit mix - are related to credit score in Linear Regression. 

Can we verify that 3 variables -listed above- will increase/decrease the chance of being in the good-standard credit score group?

Note: Question 1 and Question 3 are exactly the same. The only difference is we have used different techniques for the analysis. For question 1 we have used linear regression and question 3 logit regression for the analysis.

```{r}
## Logit Regressions for 3 variables

## Model1: poor-standard 0, good 1
df <- transform(df, Credit_Score1 = ifelse((Credit_Score==1) | (Credit_Score==2), 0, 1))
df$Credit_Score1 <- factor(df$Credit_Score1 , levels=c(0, 1))
Logit1 <- glm(Credit_Score1 ~ Monthly_Balance +Credit_History_Age+Credit_Mix, data = df, family = "binomial")
summary(Logit1)

## Model2: poor 0, standard-good 1 : We decided to use this model.
df <- transform(df, Credit_Score2 = ifelse((Credit_Score==2) | (Credit_Score==3), 1, 0))
df$Credit_Score2 <- factor(df$Credit_Score2 , levels=c(0, 1))
Logit2 <- glm(Credit_Score2 ~ Monthly_Balance +Credit_History_Age+Credit_Mix, data = df, family = "binomial")
summary(Logit2)

## Model3: poor 0, good 1
subset_logit <- subset(df, Credit_Score!=2)
subset_logit <- transform(df, Credit_Score3 = ifelse((Credit_Score==3), 1, 0))
Logit3 <- glm(Credit_Score3 ~ Monthly_Balance+Credit_History_Age+Credit_Mix, data = subset_logit, family = "binomial")
summary(Logit3)

```

## Model Evaluation: Confusion Matrix
```{r}
loadPkg("regclass")
xkabledply(confusion_matrix(Logit1), title = "Confusion matrix from Logit Model1")
xkabledply(confusion_matrix(Logit2), title = "Confusion matrix from Logit Model2")
xkabledply(confusion_matrix(Logit3), title = "Confusion matrix from Logit Model3")
unloadPkg("regclass")
```

## Model Evaluation: Hosmer and Lemeshow test  
```{r HosmerLemeshow}
#loadPkg("ResourceSelection") 
#admitLogitHoslem = hoslem.test(df$Credit_Score1, fitted(Logit1)) 
#admitLogitHoslem = hoslem.test(df$Credit_Score2, fitted(Logit2))
#admitLogitHoslem = hoslem.test(subset_logit$Credit_Score3, fitted(Logit3)) 
#unloadPkg("ResourceSelection") 

```

## Model Evaluation: Receiver-Operator-Characteristic (ROC) curve and Area-Under-Curve (AUC)
```{r}
loadPkg("pROC")

## Model1: poor-standard 0, good 1 : The model is overfitted.
#df$prob <- NA
prob=predict(Logit1, type = "response")
df$prob=prob
h <- roc(Credit_Score1~prob, data=df)
auc(h) # 0.918 area-under-curve prefer 0.8 or higher.
plot(h)

## Model2: poor 0, standard-good 1 : We decied to use this model.
prob=predict(Logit2, type = "response")
df$prob=prob
h <- roc(Credit_Score2~prob, data=df)
auc(h) # 0.77 area-under-curve prefer 0.8 or higher.
plot(h)

## Model3: poor 0, good 1 : The number of observation is below 3000.
prob=predict(Logit3, type = "response")
subset_logit$prob=prob
h3 <- roc(Credit_Score3~prob, data=subset_logit)
auc(h3) # 0.92 area-under-curve prefer 0.8 or higher.
plot(h3)

unloadPkg("pROC")
```

## Model Comparison
```{r}

## Model2: poor 0, standard-good 1
Logit2 <- glm(Credit_Score2 ~ Monthly_Balance +Credit_History_Age+Credit_Mix, data = df, family = "binomial")
summary(Logit2)
## Linear Regression
fit <- lm(Credit_Score ~ Monthly_Balance +Credit_History_Age+Credit_Mix, data = dfscale)
summary(fit)
```

# Q3 Answer
Yes, the more amounts owed, the longer length of credit history, and the good credit mix more likely to be in a good-standard group.

# SMART Question 4
Can we predict the probability of good credit score with sample information by using the best-fit model?

For example: If we know the information of Sudhanshu and Upmanyu, can we predict the probability of getting a higher credit score?
  

## Feature Selection
```{r}
loadPkg("leaps")

## Model1: poor-standard 0, good 1
subset1 = subset(df, select = -c(Credit_Score, Credit_Score2, prob))
reg.leaps <- regsubsets(Credit_Score1~., data = subset1, nbest = 1, method = "exhaustive")
plot(reg.leaps, scale = "adjr2", main = "Adjusted R^2")
plot(reg.leaps, scale = "bic", main = "BIC")
plot(reg.leaps, scale = "Cp", main = "Cp")

## Model2: poor 0, standard-good 1
subset2 = subset(df, select = -c(Credit_Score, Credit_Score1, prob))
reg.leaps <- regsubsets(Credit_Score2~., data = subset2, nbest = 1, method = "exhaustive")
plot(reg.leaps, scale = "adjr2", main = "Adjusted R^2")
plot(reg.leaps, scale = "bic", main = "BIC")
plot(reg.leaps, scale = "Cp", main = "Cp")

## Model3: poor 0, good 1
subset3 = subset(subset_logit, select = -c(Credit_Score, Credit_Score1, Credit_Score2, prob))
reg.leaps <- regsubsets(Credit_Score3~., data = subset3, nbest = 1, method = "exhaustive")
plot(reg.leaps, scale = "adjr2", main = "Adjusted R^2")
plot(reg.leaps, scale = "bic", main = "BIC")
plot(reg.leaps, scale = "Cp", main = "Cp")

#unloadPkg("leaps")
```

## Better Logit Model2 with higher adjusted R^2, lower BIC and Cp
```{r}
## Model2: poor 0, standard-good 1
# Logit Regression Based on Feature Selection Result on Adj R^2
BLogit1 <- glm(Credit_Score2 ~ Credit_Mix+Outstanding_Debt+Num_Credit_Card+Num_of_Loan+Num_Credit_Inquiries, data = subset2, family = "binomial")
summary(BLogit1)

# Logit Regression Based on Feature Selection Result on BIC
BLogit2 <- glm(Credit_Score2 ~ Outstanding_Debt+Num_Credit_Card+Num_Credit_Inquiries, data = subset2, family = "binomial")
summary(BLogit2)

# Logit Regression Based on Feature Selection Result on Cp: Let's use this logit model.
BLogit3 <- glm(Credit_Score2 ~ Credit_Mix+Credit_History_Age+Outstanding_Debt+Num_Bank_Accounts+ +Num_Credit_Card+Num_of_Loan+Num_Credit_Inquiries+Month, data = subset2, family = "binomial")
summary(BLogit3)
```

# The best logit model

```{r}
# Logit Regression Based on Feature Selection Result on BIC: Let's use this logit model.
BLogit4 <- glm(Credit_Score2 ~ Outstanding_Debt+Num_Credit_Card+Num_Credit_Inquiries, data = subset2, family = "binomial")

summary(BLogit4)
loadPkg("regclass")
xkabledply(confusion_matrix(BLogit4), title = "Confusion matrix from Logit Model4")
```


# Q4 Answer:
After the feature selection, we also built the model with higher adjusted R^2, lower BIC, and Cp. Based on the results of BIC, our best fit model shows that outstanding debt, number of credit cards, and number of credit Inquiries are statistically significant with Credit Score.

We compared the predicted probability of Sudanshu and Upmanyu. Guess whose score is higher? We see an 85.9% chance that Sudanshu will get the standard-good score otherwise Upmanyu's chance is 59.5%.

## Let's compare the predicted probability of Sudanshu and Upmanyu.

```{r}
# Sudanshu # Upmanyu
newdata <- with(subset2, data.frame(Outstanding_Debt=c(800, 500), Num_Credit_Card=c(6, 8), Num_Credit_Inquiries=c(2,10)))
predict(BLogit4, newdata, type="response")
```


```{r}
#dataset: subset2 
#y: Credit_Score2
#x: Monthly_Balance +Credit_History_Age+Credit_Mix
```


# Smart Question 5
What is optimal number of n that can be grouped out of the data so that KNN accuracy is highest? 

## KNN Analysis
K-Nearest Neighbors Algorithm. The k-nearest neighbors algorithm, also known as KNN or k-NN, is a non-parametric, supervised learning classifier, which uses proximity to make classifications or predictions about the grouping of an individual data point.

## preparing the dataset for KNN
Firstly, we are scaling all the independent continuous variables so that the knn can applied easily.
Secondly, we will fill all the nan values with the mean of the column
Thirdly, we will split the dataset into train and test. This is because 


```{r}
df_scale_logit <- data.frame(scale(df[,c("Credit_Mix","Credit_History_Age","Monthly_Balance","Num_of_Delayed_Payment","Total_EMI_per_month","Age","Outstanding_Debt","Num_Bank_Accounts","Num_Credit_Card","Num_of_Loan","Num_Credit_Inquiries","Monthly_Inhand_Salary","Amount_invested_monthly","Annual_Income","Month")]))

# df_scale_logit['Credit_Score'] = df['Credit_Score']

str(df_scale_logit)
# df_scale_logit$Credit_Score <- factor(df_scale_logit$Credit_Score)
# df_scale_logit$Credit_Score2 <- factor(df_scale_logit$Credit_Score2)
```

```{r}
library(ISLR)
library(class)
library("zoo")
df_scale_logit1 <- df_scale_logit  # Duplicate data frame
for(i in 1:ncol(df_scale_logit)) { # Replace NA in all columns
  df_scale_logit[ , i][is.na(df_scale_logit1[ , i])] <- mean(df_scale_logit1[ , i], na.rm = TRUE)
}

sample <- sample(2, nrow(df_scale_logit), replace=TRUE, prob=c(0.7,0.3))
train  <- df_scale_logit[sample==1, ]
test   <- df_scale_logit[sample==2, ]

# install.packages("zoo")         
# Install & load zoo package

df_scale_logit['Credit_Score'] = df['Credit_Score']
df_scale_logit$Credit_Score <- factor(df_scale_logit$Credit_Score)

df_scale_logit.trainlabel <- df_scale_logit[sample==1, 16]
df_scale_logit.testlabel <- df_scale_logit[sample==2, 16]

# df_scale_logit.trainlabel

knn_m1 <- knn(train = train, test = test, cl=df_scale_logit.trainlabel, k=7)

loadPkg("gmodels")
IRISPREDCross <- CrossTable(df_scale_logit.testlabel, knn_m1, prop.chisq = FALSE)
library(caret)
cm = confusionMatrix(knn_m1, reference = df_scale_logit.testlabel ) # from caret library
  # print.confusionMatrix(cm)
# df_scale_logit.testlabel

cmaccu = cm$overall['Accuracy']
print( paste("Total Accuracy = ", cmaccu ) )

cm
```

```{r}
chooseK = function(k, train_set, val_set, train_class, val_class){
  
  # Build knn with k neighbors considered.
  set.seed(1)
  class_knn = knn(train = train_set,    #<- training set cases
                  test = val_set,       #<- test set cases
                  cl = train_class,     #<- category for classification
                  k = k) #,                #<- number of neighbors considered
                  # use.all = TRUE)       #<- control ties between class assignments. If true, all distances equal to the k-th largest are included
  
  tab = table(class_knn, val_class)
  
  # Calculate the accuracy.
  accu = sum(tab[row(tab) == col(tab)]) / sum(tab)                         
  cbind(k = k, accuracy = accu)
}

# The sapply() function plugs in several values into our chooseK function.
# function(x)[function] allows you to apply a series of numbers
# to a function without running a for() loop.
knn_different_k = sapply(seq(1, 21, by = 2),  #<- set k to be odd number from 1 to 21
                         function(x) chooseK(x, 
                                             train_set = train,
                                             val_set = test,
                                             train_class = df_scale_logit.trainlabel,
                                             val_class = df_scale_logit.testlabel))

# Reformat the results to graph the results.
str(knn_different_k)
knn_different_k = data.frame(k = knn_different_k[1,],
                             accuracy = knn_different_k[2,])

# Plot accuracy vs. k.
# install.packages("ggplot2")
loadPkg("ggplot2")

ggplot(knn_different_k,
       aes(x = k, y = accuracy)) +
  geom_line(color = "red", size = 1.5) +
  geom_point(size = 3) + 
  labs(title = "Accuracy vs k-nearest-neighbour")

```

## Tree Decision
```{r}

loadPkg("rpart.plot")


# Tree Model - All Variables
# plot tree 
anova.model1 <- rpart(Credit_Score2 ~ ., data = subset2)
rpart.plot(anova.model1, main="Classification Tree for Credit_Score (All Variables)")

set.seed(1)
tree1 <- rpart(Credit_Score2 ~ ., data = subset2, method="class", control = list(maxdepth = 4) )
printcp(tree1) # display the results 
plotcp(tree1) # visualize cross-validation results 
summary(tree1) # detailed summary of splits

# create attractive postcript plot of tree 
post(tree1, file = "kythosisTree2.ps", title = "Classification Tree for Kythosis")


# Tree Model - Four Significant Variables

# plot tree 
anova.model2 <- rpart(Credit_Score2 ~ Credit_Mix+Outstanding_Debt+Num_Credit_Card+Num_Credit_Inquiries, data = subset2)
rpart.plot(anova.model2, main="Classification Tree for Credit_Score (Four Variables)")

set.seed(1)
tree2 <- rpart(Credit_Score2 ~ Credit_Mix+Outstanding_Debt+Num_Credit_Card+Num_Credit_Inquiries, data = subset2, method="class", control = list(maxdepth = 4) )
printcp(tree2) # display the results 
plotcp(tree2) # visualize cross-validation results 
summary(tree2) # detailed summary of splits

# create attractive postcript plot of tree 
post(tree2, file = "kythosisTree2.ps", title = "Classification Tree for Kythosis")

unloadPkg("rpart.plot")

```