---
title: "The Midterm Project of Thunder, Team 2"
date: "2022-10-21"
output:
  html_document:
    code_folding: hide
    number_sections: false
    toc: yes
    toc_depth: 3
    toc_float: yes
  pdf_document:
    toc: yes
    toc_depth: '3'
---

```{r init, include=FALSE}
# some of common options (and the defaults) are: 
# include=T, eval=T, echo=T, results='hide'/'asis'/'markup',..., collapse=F, warning=T, message=T, error=T, cache=T, fig.width=6, fig.height=4, fig.dim=c(6,4) #inches, fig.align='left'/'center','right', 
library(ezids)
# knitr::opts_chunk$set(warning = F, results = "markup", message = F)
knitr::opts_chunk$set(warning = F, results = "hide", message = F)
options(scientific=T, digits = 3) 
# options(scipen=9, digits = 3) 
# ‘scipen’: integer. A penalty to be applied when deciding to print numeric values in fixed or exponential notation.  Positive values bias towards fixed and negative towards scientific notation: fixed notation will be preferred unless it is more than ‘scipen’ digits wider.
# use scipen=999 to prevent scientific notation at all times
```

# Data
### Loading the Raw Dataset 
```{r echo = FALSE, results = "asis"}
# Use libraries
library(ezids)
library(knitr)
library(magrittr)
library(dplyr)
library(purrr)
library(tidyr)
library(stringr)
library(ggplot2)


# Load Data
midterm = data.frame(read.csv("dataset/train.csv"))
# Use "January" 
midterm2 = subset(midterm, Month=="January")

kable(midterm2[1:5,], "pipe")
```

### Raw Data Structure
```{r echo = FALSE, results = "asis"}
data.frame(variable = names(midterm2),
           classe = sapply(midterm2, typeof),
           first_values = sapply(midterm2, function(x) paste0(head(x),  collapse = ", ")),
           row.names = NULL) %>%
  kable()
```

### Raw Data Summary
```{r echo = FALSE, results = "asis"}
xkabledply(summary(midterm2))

### for the future analysis
#midterm2_subset <- midterm2[ , names(midterm2) %in% c("ID", "Name", "Age", "Annual_Income", "Num_Bank_Accounts", "Num_Credit_Card", "Interest_Rate", "Num_of_Loan", "Num_of_Delayed_Payment", "Credit_Mix", "Total_EMI_per_month", "Monthly_Balance", "Credit_Score")]
#str(midterm2_subset)
#summary(midterm2_subset)
#nrow(midterm2_subset)
```

### Subset Raw Data
```{r echo = FALSE, results = "asis"}
# Subset Data including 5 variables
midterm2_subset <- midterm2[ , names(midterm2) %in% c("Age", "Num_of_Delayed_Payment", "Credit_Mix", "Total_EMI_per_month", "Credit_Score")]
```

### Data Cleaning: Remove NA and Convert data type

```{r Brooklyn_1}
# "Age"
# Removed Special Characters & Changed the data type into "int"
midterm2_subset$Age <- gsub("[[:punct:]]", "", midterm2_subset$Age)
midterm2_subset$Age <- as.integer(midterm2_subset$Age)

### for the future analysis
# "Annual_Income"
# Removed Special Characters & Changed the data type into "num" & Rounded
# midterm2_subset$Annual_Income <- as.numeric(sub("_", "", midterm2_subset$Annual_Income))

```

```{r HaeLee_1}
# "Num_of_Delayed_Payment"
# Removed Special Characters & Changed the data type from "char" to "int"
midterm2_subset$Num_of_Delayed_Payment <- gsub("[[:punct:]]", "", midterm2_subset$Num_of_Delayed_Payment)
midterm2_subset$Num_of_Delayed_Payment <- as.integer(midterm2_subset$Num_of_Delayed_Payment)

### for the future analysis
# "Num_of_Loan" 
# Removed Special Characters & Changed the data type from "char" to "int"
# midterm2_subset$Num_of_Loan <- gsub("[[:punct:]]", "", midterm2_subset$Num_of_Loan)
# midterm2_subset$Num_of_Loan <- as.integer(midterm2_subset$Num_of_Loan)

# "Num_of_Loan"
# Removed value below 0 
# midterm2_subset <- midterm2_subset[midterm2_subset['Num_of_Loan'] >= 0, ]
```

```{r Upmanyu_1}
# "Credit_Mix"
# Removed Special Characters 
# Converted "char" into "int" from "Good" to 3, "Standard" to 2, and "Bad" to 1
midterm2_subset <- midterm2_subset[midterm2_subset['Credit_Mix'] != "_",]
midterm2_subset$Credit_Mix[midterm2_subset$Credit_Mix == 'Bad'] <- 1
midterm2_subset$Credit_Mix[midterm2_subset$Credit_Mix == 'Standard'] <- 2
midterm2_subset$Credit_Mix[midterm2_subset$Credit_Mix == 'Good'] <- 3
midterm2_subset$Credit_Mix <- as.integer(midterm2_subset$Credit_Mix)
```

```{r Sudhanshu_1}
# Rounded "Total_EMI_per_month"
midterm2_subset["Total_EMI_per_month"] <- 
round(midterm2_subset["Total_EMI_per_month"], digits = 2)

# "Credit_score"
# Removed Special Characters
midterm2_subset <- midterm2_subset[midterm2_subset['Credit_Score'] != "_",]
# Convert Credit Score into Factor Variable\
midterm2_subset$Credit_Score <- factor(midterm2_subset$Credit_Score , levels=c('Poor', 'Standard', 'Good'))

### for the future analysis
# "Monthly_Balance"
# Converted into "int" and rounded 
# midterm2_subset$Monthly_Balance <- as.integer(midterm2_subset$Monthly_Balance)
# midterm2_subset["Monthly_Balance"] <- round(midterm2_subset["Monthly_Balance"], digits = 2)
```

```{r Upmanyu_2}
# Removed NA from data
midterm2_subset = na.omit(midterm2_subset)
# Filtered out a group age under 18 and greater than 100
midterm2_subset<-midterm2_subset[(midterm2_subset$Age > 17) & (midterm2_subset$Age < 100),]
```

### Removed Outliers 
```{r}
df = outlierKD2(midterm2_subset, Num_of_Delayed_Payment, rm=T)
df = outlierKD2(df, Total_EMI_per_month, rm=T)
df = outlierKD2(df, Age, rm=T)
```

## Descriptive Statistics 

### Data Structure
```{r echo = FALSE, results = "asis"}
data.frame(variable = names(df),
           classe = sapply(df, typeof),
           first_values = sapply(df, function(x) paste0(head(x),  collapse = ", ")),
           row.names = NULL) %>%
  kable()
```

### Data Summary
```{r echo = FALSE, results = "asis"}
xkabledply(summary(df))

### for the future analysis
#midterm2_subset <- midterm2[ , names(midterm2) %in% c("ID", "Name", "Age", "Annual_Income", "Num_Bank_Accounts", "Num_Credit_Card", "Interest_Rate", "Num_of_Loan", "Num_of_Delayed_Payment", "Credit_Mix", "Total_EMI_per_month", "Monthly_Balance", "Credit_Score")]
#str(midterm2_subset)
#summary(midterm2_subset)
#nrow(midterm2_subset)
```


# EDA
## Analysis for Credit Mix by Brooklyn

### Histogram of Credit Mix
```{r Brooklyn_4}
ggplot(df, aes(x=Credit_Mix, fill = Credit_Score)) + geom_histogram(binwidth = 1) + ggtitle ("Credit_Mix") + xlab("Credit_Mix") + ylab("Total count")
```

### Chi-square Test for Credit Mix and Credit Score
Whether Credit_Mix and Credit_Score are likely to be related or not

```{r echo = FALSE, results = "asis"}
# The Chi-square test of independence
# check whether Credit_Mix and Credit_Score are likely to be related or not
# The independence test tells us only whether there is a relationship or not; it does not tell us that one variable causes the other

mix = table(df$Credit_Mix, df$Credit_Score)
rownames(mix) <- c("Bad","Standard","Good")
xkabledply(mix, title="Contingency table for Credit_Mix vs Credit_Score")

chitest = chisq.test(mix)
print(chitest)

# expected values
xkabledply(chitest$expected, title = "Cross table for the expected frequencies between Credit_Mix and Credit_Score")

```

## Analysis for Number of Delayed Payment by HaeLee
Separated three subsets for poor, standard, and good in Credit Score
```{r HaeLee_3}
#str(df)
#summary(df)
#xkabledply(summary(df), title = "Summary of the Refined Dataset")

Poor = subset(df, df$Credit_Score == 'Poor')
summary(Poor)
Standard = subset(df, df$Credit_Score == 'Standard')
summary(Standard)
Good = subset(df, df$Credit_Score == 'Good')
summary(Good)
```

### T-test at 0.95 Confidence Level for the Number of Delayed Payment
```{r HaeLee_4}
# Construct t-intervals for the Number of Delayed Payment
# All Groups
delay_All = t.test(x=df$Num_of_Delayed_Payment)
delay_All
# Poor Group
delay_Poor = t.test(x=Poor$Num_of_Delayed_Payment)
delay_Poor
# Standard Group
delay_Standard = t.test(x=Standard$Num_of_Delayed_Payment)
delay_Standard
# Good Group
delay_Good = t.test(x=Good$Num_of_Delayed_Payment)
delay_Good
```
Result: All are rejected since p-value are below 0.05, which means that each true mean is not equal to 0.

### Boxplot for the Number of Delayed Payment
```{r HaeLee_5}
ggplot(df, aes(x=Credit_Score, y=Num_of_Delayed_Payment)) + geom_boxplot( colour=c("red","green","blue")) +
  labs(title="Boxplot of the Number of Delayed Payment with different Credit Scores", x="Credit Score", y = "Number of Delayed Payment")
```

### Histogram for the Number of Delayed Payment
```{r HaeLee_6}
# All Groups by colors
ggplot(df, aes(x=Num_of_Delayed_Payment, fill = Credit_Score)) + geom_histogram(binwidth = 1) + ggtitle ("Histogram of the Number of Delayed Payment") + xlab("Number of Delayed Payment") + ylab("Total count")
# All Groups
ggplot(df, aes(Num_of_Delayed_Payment)) + geom_histogram(fill="yellow") + ggtitle("Histogram of the Number of Delayed Payment") 
# Poor Group
ggplot(Poor, aes(Num_of_Delayed_Payment)) + geom_histogram(fill="red") + ggtitle("Histogram of the Number of Delayed Payment in Poor Credit Score Group") + xlab("Number of Delayed Payment in Poor Group")
# Standard Group
ggplot(Standard, aes(Num_of_Delayed_Payment)) + geom_histogram(fill="green") + ggtitle("Histogram of Number of Delayed Payment in Standard Credit Score Group") + xlab("Number of Delayed Payment in Standard Group")
# Good Group
ggplot(Good, aes(Num_of_Delayed_Payment)) + geom_histogram(fill="blue") + ggtitle("Histogram of Number of Delayed Payment in Good Credit Score Group") + xlab("Number of Delayed Payment in Good Group")

## Check for normality on the Number of Delayed Payment, a numerical variable by using histogram and QQ-plot
```

### QQ-Plot with QQ line for the Number of Delayed Payment
```{r HaeLee_7}
# All Group
qqnorm(df$Num_of_Delayed_Payment, col="dodgerblue2", main="QQ-plot of the Number of Delayed Payment")
qqline(df$Num_of_Delayed_Payment)
# Poor Group
qqnorm(Poor$Num_of_Delayed_Payment, col="red", main="QQ-plot of the Number of Delayed Payment in Poor Credit Score Group")
qqline(Poor$Num_of_Delayed_Payment)
# Standard Group
qqnorm(Poor$Num_of_Delayed_Payment, col="green", main="QQ-plot of the Number of Delayed Payment in Standard Credit Score Group")
qqline(Poor$Num_of_Delayed_Payment)
# Good Group
qqnorm(Poor$Num_of_Delayed_Payment, col="blue", main="QQ-plot of the Number of Delayed Payment in Good Credit Score Group")
qqline(Poor$Num_of_Delayed_Payment)
```

### ANOVA for the Number of Delayed Payment
```{r HaeLee_8}
# Does the three subgroups have different the Number of Delayed Payment average?
anova_delayed = aov(Num_of_Delayed_Payment ~ Credit_Score, data=df)
anova_delayed
names(anova_delayed)
xkabledply(anova_delayed, title = "ANOVA result summary the Number of Delayed Payment between Credit Score")
```
Result: P-value is below 0.05 and reject the Null. Therefore, we can say that credit scores from three different group are significantly different from others and have not same average number of delayed payment.

### Post-hoc Tukey HSD for the Number of Delayed Payment
```{r HaeLee_9}
# Since they are not all the same, we need to follow up with a post-hoc test.
tukeyAoV <- TukeyHSD(anova_delayed)
tukeyAoV
```
Result: As we visually observed from box plots, now confirmed with the turkey results, treatment 1, 2, and 3 are pairwise considered having significantly different means at 0.05 level.

## Analysis for Number of Delayed Payment by Sudhanshu
### Removed Outliers and divded EMI into two subsets, zero EMI group and non-zero EMI group 
```{r Sudhanshu_2}
# EDA for Total EMI
zero_emi <- subset(df, Total_EMI_per_month == 0)
str(zero_emi)
non_zero_emi <- subset(df, Total_EMI_per_month != 0)
```

### T-test at 0.95 Confidence Level for the Total EMI per Month
```{r Sudhanshu_3}
Total_Emi = t.test(x=df$Total_EMI_per_month)
Total_Emi

non_zero_emi_t = t.test(x=non_zero_emi$Total_EMI_per_month)
non_zero_emi_t
```
Result: All are rejected since p-value are below 0.05, which means that each true mean is not equal to 0.

### Boxplot for the Total EMI per month
```{r Sudhanshu_4}
ggplot(df, aes(x=Credit_Score, y=Total_EMI_per_month)) + geom_boxplot( colour=c("red","green","blue")) +
  labs(title="Boxplot of the Total EMI per month with different Credit Scores", x="Credit Score", y = "Number Total_EMI_per_month")
# ggplot(non_zero_emi, aes(x=Credit_Score, y=Total_EMI_per_month)) + geom_boxplot( colour=c("red","green","blue")) +
  #labs(title="Boxplot of the Total EMI per month with different Credit Scores", x="Credit Score", y = "Number Total_EMI_per_month Delayed Payment for Non Zero Group")
```

### Histogram for the Total EMI per month
```{r Sudhanshu_5}
# All Groups by colors

ggplot(df, aes(x=Total_EMI_per_month, fill = Credit_Score)) + geom_histogram(binwidth = 1) + ggtitle ("Histogram of the Total EMI per Month") + xlab("Total EMI per Month") + ylab("Total count")
# EMI Zero Group 
ggplot(zero_emi, aes(x=Total_EMI_per_month, fill = Credit_Score)) + geom_histogram(binwidth = 1) + ggtitle ("Histogram of the Total EMI per Month") + xlab("Total EMI per Month") + ylab("Total count")
# EMI Non-Zero Group
ggplot(non_zero_emi, aes(x=Total_EMI_per_month, fill = Credit_Score)) + geom_histogram(binwidth = 1) + ggtitle ("Histogram of the Total EMI per Month") + xlab("Total EMI per Month") + ylab("Total count")

```

### QQ-Plot with QQ line for the Total EMI per month
```{r sudhanshu_6}
# All Group
qqnorm(df$Total_EMI_per_month, col="dodgerblue2", main="QQ-plot of the Total EMI per month")
qqline(df$Total_EMI_per_month)
# Zero EMI Group
qqnorm(zero_emi$Total_EMI_per_month, col="red", main="QQ-plot of the Total EMI per month in zero EMI Group")
qqline(zero_emi$Total_EMI_per_month)
# Non zero Group
qqnorm(non_zero_emi$Total_EMI_per_month, col="green", main="QQ-plot of the Total EMI per month in non zero EMI Group")
qqline(non_zero_emi$Total_EMI_per_month)
```

### ANOVA for the Total EMI per month
```{r sudhanshu_7}
# Does the three subgroups have different the Number of Delayed Payment average?
# All Group
anova_toal_emi = aov(Total_EMI_per_month ~ Credit_Score, data=df)
anova_toal_emi
names(anova_toal_emi)
xkabledply(anova_toal_emi, title = "ANOVA result summary total EMI per month between Credit Score")
# Non Zero Group
anova_nonzero_emi = aov(Total_EMI_per_month ~ Credit_Score, data=non_zero_emi)
anova_nonzero_emi
names(anova_nonzero_emi)
xkabledply(anova_nonzero_emi, title = "ANOVA result summary total EMI per month between Credit Score")
```

### Post-hoc Tukey HSD for the Total EMI per month
```{r sudhanshu_8}
# Since they are not all the same, we need to follow up with a post-hoc test.
# All group
tukeyAoVemi_All <- TukeyHSD(anova_toal_emi)
tukeyAoVemi_All

tukeyAoVemi_NonEMI <- TukeyHSD(anova_nonzero_emi)
tukeyAoVemi_NonEMI
```



# Annual Income
# 1. Less than 100,000
# 2. More than 100,000
```{r Upmanyu}
library(ggplot2)
midterm2_subset$Credit_Score <- as.factor(midterm2_subset$Credit_Score)
midterm2_subset$Credit_Mix <- as.factor(midterm2_subset$Credit_Mix)



# EDA for Number of Loan
df = outlierKD2(df, Age, rm=T)
```

## Analysis for Age by Upmanyu



# Histogram for Age

### Histogram for Age

```{r Upmanyu_4}
# library(VGAM)
# All Groups
ggplot(df, aes(x=Age, fill = Credit_Score)) + geom_histogram(bins=8) + ggtitle ("Histogram of the Age") + xlab("Age") + ylab("Total count")

# Poor Group
ggplot(df[df['Credit_Score']=='Poor',], aes(Age)) + geom_histogram(fill="red",bins = 8) + ggtitle("Histogram of the Age in Poor Credit Score Group") + xlab("Age in Poor Group")


# Standard Group
ggplot(df[df['Credit_Score']=='Standard',], aes(Age)) + geom_histogram(fill="green",bins = 8) + ggtitle("Histogram of Age in Standard Credit Score Group") + xlab("Age in Standard Group")

# Good Group
ggplot(df[df['Credit_Score']=='Good',], aes(Age)) + geom_histogram(fill="blue",bins=8) + ggtitle("Histogram of Age in Good Credit Score Group") + xlab("Age in Good Group")
```

### Boxplot for Age
```{r Upmanyu_5}
ggplot(df, aes(x=Credit_Score, y=Age)) + geom_boxplot( colour=c("red","green","blue")) +
  labs(title="Boxplot of the Age", x="Credit Score", y = "Age")
```

### ANOVA for Age
```{r Upmanyu_6}
anova_delayed1 = aov(Age ~ Credit_Score, data=df)
anova_delayed1
names(anova_delayed1)
xkabledply(anova_delayed1, title = "ANOVA result summary the Age between Credit Score")
```

### Post-hoc Tukey HSD for Age
```{r Upmanyu_7}
tukeyAoV1 <- TukeyHSD(anova_delayed)
tukeyAoV1
```


```{r}
set_more_income = midterm2_subset[midterm2_subset['Annual_Income']<100000,]
ggplot(
  set_more_income,
  aes(y = Annual_Income, x = Num_of_Delayed_Payment))+geom_point(aes(color = factor(Credit_Score)))

```

```{r}
str(df)
#summary(df)
xkabledply(summary(df), title = "Summary of the Refined Dataset")

Poor = subset(df, df$Credit_Score == 'Poor')
summary(Poor)
Standard = subset(df, df$Credit_Score == 'Standard')
summary(Standard)
Good = subset(df, df$Credit_Score == 'Good')
summary(Good)


```

